Network Trait marker for working memory deficit in Schizophrenia: a multi site study

### 2016-02-24 manuscript.tex
a little progress
a little progress

\usepackage{color}
\usepackage{multirow,booktabs,ctable,array}
\usepackage{lscape}
\usepackage{amsmath}
\usepackage{lineno}
\usepackage{ulem}
\usepackage{setspace}
\usepackage{listings}
\usepackage{float}

@@

Working memory is typically defined as the ability to maintain and manipulate information over short periods of time. WM has been shown to be impaired in many neurological and psychiatric syndromes including Schizophrenia. It was thought to be tightly associated with cognitive deficits in Schizophrenia (Green 2000). A large body of work has demonstrated that individuals with schizophrenia have deficits in working memory (Goldman-Rakic, 1991; Park and Holzman, 1992). These study may shed light on the treatment of Schizophrenia. However, there's still no conclusions on the pathology of WM. This may be due to the heterogeneous configurations of tasks and the small sample sizes of the most imaging studies. To overcome this, we assess the resting connectivity of core WM netwroks in a muti-site study framework. This study may provide us with insight into the causes, progression and treatment of Schizophrenia. WM itself is a complex process which has been multidimensionally related to the psychosis. Thus, an examination of the underlying neurological mechanism provided us with insight into the causes, progression and even treatment of schizophrenia.

There has been abundant imaging studies on WM deficits in Schizophrenia, but the differences among the tasks and material make it difficult to make a conclusion. There have been evidence of multi-modality deficits: visual spatial, visual object, verbal, and other types of working memory. One popular and original model of WM is a system encoding and maintaining modality-specific short-term memory and central executive component to manipulate the information. Some studies have found evidence for different patterns of functional connectivity during different working memory task conditions (e.g., as a function of load, stimulus type, or task phase).  Such findings suggest that functional connectivity changes could reflect differences in task engagement or responsivity of brain networks to modulation,rather than stable changes that persist across all task states. Some studies have found both impairments in the modality-specific perception component and the later manipulation component. It is widely agreed that WM involves several different component processes. In a recent meta analysis, the author draw attention to a consistent and restricted "core network" emerged from conjunctions across analyses of specific task designs and contrasts. This distributed network was believed to be active in WM task ignoring the task type , stimulus type and WM load and may be act as a base part in WM.

@@

The resting state fMRI data presented here was collected from six hospitals in China which participated in the Brainnetome Project for Schizophrenia. The six hospitals are  Patients and controls are matched as much as possible for age, sex, handedness, and race distributions with each site. Peking University Sixth Hospital (PKUH6); Beijing Huilongguan Hospital (HLG); Xijing Hospital (XJ); Henan Mental Hospital (HM);  Renmin Hospital of Wuhan University (RWU); and Zhumadian Psychiatric Hospital (ZMD). Henan Mental Hospital provided two distinct MRI scanners: Siemens (HMS) and General Electric (HMG), for a total of eight scanning centers. The study at each center was approved by the local ethical review board. All the participants provided written informed consent.

@@

Two types of 3 T MRI scanners (four Siemens, three General Electric) were used at the participating centers. To ensure equivalent data acquisition protocol and high quality imaging data, the scanning parameters of the functional scans at each of the six centers were set up by an experienced researcher before data acquisition. An echo planar imaging sequence was used to obtain the
functional images, the parameters were as follows: 30 axial slices, TR = 2000 ms, TE = 30 ms, matrix = 64 × 64, flip angle = 90°, FOV = 240*240 mm 2, slice thickness = 4 mm, gap = 0.4 mm. A total of 250 brain volumes were collected, resulting in a total scan time of 500 s.The MRI scan sequences and parameters for each center are listed in eTable 1. To be noticed, the time point number of the images from ZMD is 180 and is different from the 240 of the other sites. We did not exclude this site since we are eager to keep as much data and sites as possible, to support the validation of the multi-site analysis.

@@

The iamges were preprocessed with a based in-house software: Brainnetome Toolkit which utilized Statistical Parametric Mapping SPM8 (http://www.fil.ion.ucl.ac.uk/spm). The pipeline includes the following steps: The first ten images were deleted for the signal equilibration. The remaining iamges were conducted for slice acquisition correction and head motion correction.  The fMRI data which had
less than 3.0 mm of head motion and 3.0° of angular rotation were included.  Moreover, the mean frame-wise displacement (FD) was computed by averaging FDi from every time point for each subject. There were no differences for the mean FD between groups
( t = 0.413, p = 0.682) (Table 1). Then the fMRI images were normalized to the standard Montreal Neurological Institute (MNI) template provided by SPM and resample to the 3-mm isotropic voxels. Artefacts due to changes in global, ventricle and white matter signals, residual motion were removed using voxel-wise regression. A temporal filter (0.01 Hz < f < 0.08 Hz) were used to reduce the low-frequency drift and physiological high frequency respiratory and cardiac noise.  Finally, the data was smoothed with an isotropic Gaussian kernel of 6 mm full-width at half-maximum.

@@

@@

To perform the fcMRI analyses, time series from the resting-state scan were extracted by averaging the time series of all voxels in each ROI. The resulting time series of each ROI were then entered into the following connectivity analyses.
The Pearson (full) correlation coefficient was used to estimate functional connectivity between each pair of time series. A Fisher Z transform

@@

\section*{Discussion}

>>>>

\usepackage{color}
\usepackage{multirow,booktabs,ctable,array}
\usepackage{lscape}
\usepackage{amsmath}
\usepackage{lineno}
\usepackage{ulem}
\usepackage{setspace}
\usepackage{listings}
\usepackage{float}
\usepackage{url}

@@

Working memory is typically defined as the ability to maintain and manipulate information over short periods of time. WM has been shown to be impaired in many neurological and psychiatric syndromes including Schizophrenia. It was thought to be tightly associated with cognitive deficits in Schizophrenia (Green 2000). A large body of work has demonstrated that individuals with schizophrenia have deficits in working memory (Goldman-Rakic, 1991; Park and Holzman, 1992). These study may shed light on the treatment of Schizophrenia. However, there's still no conclusions on the pathology of WM. This may be due to the heterogeneous configurations of tasks and the small sample sizes of the most imaging studies. To overcome this, we assess the resting connectivity of core WM netwroks in a muti-site study framework. Such experiment configuration would help to find stable trait impairment in Schizophrenia, desregarding their age,sex, disease progress etc. This study may provide us with insight into the causes, progression and treatment of Schizophrenia. WM itself is a complex process which has been multidimensionally related to the psychosis. Thus, an examination of the underlying neurological mechanism provided us with insight into the causes, progression and even treatment of schizophrenia.

There has been abundant imaging studies on WM deficits in Schizophrenia, but the differences among the tasks and material make it difficult to make a conclusion.  Some studies have found evidence for different patterns of functional connectivity during different working memory task conditions (e.g., as a function of load, stimulus type, or task phase). Such findings suggest that functional connectivity changes could reflect differences in task engagement or responsivity of brain networks to modulation,rather than stable changes that persist across all task states. On the other hand, working memory itself is a complex system which consist of different components. It is widely agreed that WM involves several different component processes. One popular and original model of WM is a system encoding and maintaining modality-specific short-term memory and central executive component to manipulate the information. Some studies have found both impairments in the modality-specific perception component and the later manipulation component. There have been evidence of multi-modality deficits: visual spatial, visual object, verbal, and other types of working memory. In a recent meta analysis, the author draw attention to a consistent and restricted "core network" emerged from conjunctions across analyses of specific task designs and contrasts. This distributed network was believed to be active in WM task ignoring the task type , stimulus type and WM load and may be act as a base part in WM. We restrict our analysis in these core networks.

@@

The resting state fMRI data presented here was collected from six hospitals in China which participated in the Brainnetome Project for Schizophrenia. The six hospitals are Peking University Sixth Hospital (PKUH6); Beijing Huilongguan Hospital (HLG); Xijing Hospital (XJ); Henan Mental Hospital (HM);  Renmin Hospital of Wuhan University (RWU); and Zhumadian Psychiatric Hospital (ZMD). Henan Mental Hospital provided two distinct MRI scanners: Siemens (HMS) and General Electric (HMG), for a total of eight scanning centers. Patients and controls are matched as much as possible for age, sex, handedness, and race distributions within each site. The study at each center was approved by the local ethical review board. All the participants provided written informed consent.

@@

Two types of 3T MRI scanners (four Siemens, three General Electric) were used at the participating centers (details in table \#). To ensure equivalent data acquisition protocol and high quality imaging data, the scanning parameters of the functional scans at each of the six centers were set up by an experienced researcher before data acquisition. An echo planar imaging sequence was used to obtain the functional images, the parameters were as follows: 30 axial slices, TR = 2000 ms, TE = 30 ms, matrix = 64 × 64, flip angle = 90°, FOV = 240*240 mm 2, slice thickness = 4 mm, gap = 0.4 mm. A total of 250 brain volumes were collected, resulting in a total scan time of 500s. The MRI scan sequences and parameters for each center are listed in eTable 1. To be noticed, the time point number of the images from ZMD is 180 and is different from the 240 of the other sites. We did not exclude this site since we are eager to keep as much data and sites as possible, to support the validation of the multi-site analysis. The multi-site statisical stratergy we used is robust to various of volum numbers in different sites.

@@

The iamges were preprocessed with a based in-house software: Brainnetome Toolkit which utilized Statistical Parametric Mapping SPM8 (\url{http://www.fil.ion.ucl.ac.uk/spm}). The pipeline includes the following steps: The first ten images were deleted for the signal equilibration. The remaining iamges were conducted for slice acquisition correction and head motion correction.  The fMRI data which had
less than 3.0mm of head motion and 3.0° of angular rotation were included.  Moreover, the mean frame-wise displacement (FD) was computed by averaging FD\_i from every time point for each subject. There were no differences for the mean FD between groups ( t = 0.413, p = 0.682) (Table 1). Then the fMRI images were normalized to the standard Montreal Neurological Institute (MNI) template provided by SPM and resample to the 3-mm isotropic voxels. Artefacts due to changes in global, ventricle and white matter signals, residual motion were removed using voxel-wise regression. A temporal filter (0.01 Hz \textless f \textless 0.08 Hz) were used to reduce the low-frequency drift and physiological high frequency respiratory and cardiac noise. Finally, the data was smoothed with an isotropic Gaussian kernel of 6 mm full-width at half-maximum.

@@

The ROIs in this study were extracted from a previous meta analysis by Simon, in which they find regions that commonly acvite during various working memory tasks. A consistent and restricted "core" network emerged from conjunctions across analyses of specific task designs and contrasts: task effects for n-back and Sternberg tasks, verbal and non-verbal tasks, load effects and all three task components (encoding, maintenance, recall). These regions includs dosal area 44 , anterior insula, (pre-) SMA, and IPS, bilaterally. The peak coordinates are listed in table \#. A 5mm radis sphrere ROIs are created form these peak coordinates in MNI standard space.

@@

To perform the fcMRI analyses, time series from the resting-state scan were extracted by averaging the time series of all voxels in each ROI. The resulting time series of each ROI were then entered into the following connectivity analyses. The Pearson (full) correlation coefficient was used to estimate functional connectivity between each pair of time series. A Fisher Z transform was applied to transform from pearson r to z scores.

@@

Association analysis

We did not find any association between the FC and the clinical scores.
\section*{Discussion}
